\bf Faster Neural Machine Translation Inference

### 2018-01-27 fast-beam/fast-beam.tex
fast beam paper

Thirdly, we are only interested in the probability of the best class. Since we have precalculated the best class in Figure~\ref{algo:Calculate softmax}, we shall only calculate softmax for this one class, avoiding the computational and memory bandwith of computing the probability for all classes. The outline of the our function is shown in Figure~\ref{algo:Fused Kernel}.

@@

\COMMENT{calculate softmax($p_i$)}
\RETURN $\frac{1}{sum}$, $best$

@@

In fact, we are usually only interested in the argmax class during inference, not the probability. Therefore, we can skip the second iteration over $p$ and avoid computing the softmax altogether. %, Figure~\ref{algo:Argmax only}.

>>>>

Thirdly, we are only interested in the best class. Since the best class is known, we can avoid calculating softmax for all classes. The outline of the our function is shown in Figure~\ref{algo:Fused Kernel}.

@@

\RETURN $\frac{1}{sum}$, $best$

@@

In fact, we are usually only interested in the best class during inference, not the probability. Therefore, we can skip the second iteration over $p$ in Figure~\ref{algo:Fused Kernel} and avoid computing the softmax altogether. %, Figure~\ref{algo:Argmax only}.
